The LSST DESC 3x2pt Tomography Optimization Challenge

### 2021-03-15 paper/paper.tex
bugs and more concl

\begin{figure*}
\includegraphics[width=0.9\linewidth]{results/g_band_loss.pdf}
\caption{The degradation in constraining power over all methods
 when comparing them on methods including and excluding
the g-band, in terms of the ratio of the $w_0-w-a$ figure of merit.  The left-hand panel shows
results for the CosmoDC2 scenarios, and the right-hand panel for the Buzzard scenarios.  Colours
indicate the number of bins used in the analysis.}
\label{fig:loss}
\end{figure*}

@@

Notably, though, the winning CosmoDC2 \textsc{funbins} method used the simpler approach desribed above. The 
success of this simple and fast solution suggests this as an easy heuristic for well-optimized nominal edges, 
at least for cases where clustering-like metrics are important.  Its relatively lower
scores on the Buzzard metrics, as noted in \authoref{sec:metric-results}, does however further highlight
the importance of science- and sample-specific training.

@@

>>>>

\begin{figure*}
\includegraphics[width=0.9\linewidth]{results/g_band_loss.pdf}
\caption{The degradation in constraining power over all methods
 when comparing them on methods including and excluding
the g-band, in terms of the ratio of the $w_0-w_a$ figure of merit.  The left-hand panel shows
results for the CosmoDC2 scenarios, and the right-hand panel for the Buzzard scenarios.  Colours
indicate the number of bins used in the analysis.}
\label{fig:loss}
\end{figure*}

@@

Notably, though, the winning CosmoDC2 \textsc{funbins} method used the simpler approach desribed above. The 
success of this simple and fast solution suggests this as an easy heuristic for well-optimized nominal edges, 
at least for cases where clustering-like metrics are important.  Its relatively lower
scores on the Buzzard metrics, as noted in \autoref{sec:metric-results}, does however further highlight
the importance of science- and sample-specific training.

@@

The wide range in scores for nominally similar methods (for example, the several methods using
neural network approaches) reminds us that, generically, the implementation details of machine
learning methods can drastically affect their performance.
